Approximation as Differentiation notes

### 2025-02-09 notes.tex
Category of families.

This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C \to
\Set$. (Where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete categories.)

>>>>

For a functor $F: C \to Set$, we have the category where:
\begin{itemize}
\item objects are pairs $(A, x)$ where $x \in FA$
\item morphisms from $(A, x)$ to $(B, y)$ are morphisms $f: A \to B$ in $C$ where $(Ff)(x) = y$
\end{itemize}

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C
\to \Set$. (Where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete
categories.
